Are We Reusing Outdated and Licensed Code from Stack Overflow?

### 2017-02-19 cloneoverflow-latex/cloneoverflow.tex
Reworked RQ1 again. Rewrote the abstract. Other small changes.

@@

\begin{abstract}
	We studied online code clones on the popular programming Q\&A website, Stack Overflow, and their issues on outdated code and software licensing violation. Online code clones are code fragments that are copied from software projects or online sources to Stack Overflow as examples. They can be discovered by using code clone detectors, yet they are inherently different from normal code clones in software projects in several aspects. Due to an absence of checking mechanism after the code has been copied to Stack Overflow, the online code clones may suffer from being outdated and violating the original software license. %Moreover, we also found that majority of online code clones do not contain the license of their originals. 
	We designed the experiment incorporating several state-of-the-art tools and techniques to automatically extract, prioritise, and filter the clones. As a result, we discovered 51,926 non-trivial online clone candidates between 144,064 Java code snippets on Stack Overflow and 111 Java open source projects in the curated Qualitas corpus. The manual study of the 3,632 online clone pairs revealed that 64 clones on Stack Overflow are outdated. Furthermore, we found 357 Stack Overflow code snippets that do not contain software license of their originals or have conflicting licenses. These snippets are questionable for reuse. Our study is among the first to address the problem of outdated and license-violating code snippets on Stack Overflow.
\end{abstract}

@@

\begin{figure*}
	\begin{lstlisting}
          /* Code in Stack Overflow post ID 22315734 */                  /* WritableComparator.java (2016-09-26) */
          public int compare(byte[] b1,int s1,int l1,                    public int compare(byte[] b1,int s1,int l1,
                             byte[] b2,int s2,int l2) {                                     byte[] b2,int s2,int l2) {
            try {                                                          try {
              buffer.reset(b1,s1,l1); /* parse key1 */                       buffer.reset(b1,s1,l1); /* parse key1 */
              key1.readFields(buffer);                                       key1.readFields(buffer);
              buffer.reset(b2,s2,l2); /* parse key2 */                       buffer.reset(b2,s2,l2); /* parse key2 */
              key2.readFields(buffer);                                       key2.readFields(buffer);
            } catch (IOException e) {                                        buffer.reset(null,0,0); /* clean up reference */
              throw new RuntimeException(e);                               } catch (IOException e) {
            }                                                                throw new RuntimeException(e);
            return compare(key1,key2); /* compare them */                  }
          }                                                                return compare(key1, key2); /* compare them */
	                                                                       }
	\end{lstlisting}
	\caption{A motivating example of the two code fragments of
          {\small\texttt{WritableComparator.java}}. The one from the
          Stack Overflow post 22315734 (left) is outdated when compared to
          its latest version in the \textsf{hadoop} code base
          (right).}
	\label{fig:before-after}
\end{figure*}

@@

While research has mostly focused on reusing code snippets \emph{from}
Stack Overflow (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less work
has been conducted on finding the origins of code examples copied
\emph{to} Stack Overflow and problems of reusing them such as outdated
code and software licensing violations. This paper makes the following
primary contributions:

@@

\noindent%
The \textit{good-value}  and the \textit{ok-value}  of two clone pairs are then defined as
%\squeezeup
\begin{align*}
	good(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = min(overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1), \\ overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2))
\end{align*}
\begin{align*}
	ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) = min(max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1),~~ \\ contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1)),~
	\\ max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2),~~ \\contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2)))
\end{align*}

@@

Even choosing only the default configurations, the number of disagreed
clone pair candidates is still too large for manual inspection (67,570
for $S_D$ and 632,855 pairs for $N_D$). We applied three filters: clone
size, irrelevant methods, similarity threshold, and good/ok pairs. For
the \emph{clone size filter}, we raised the minimum clone size to 10 lines
since larger clones are more interesting, while smaller ones tend to
be false clones~\cite{Saini2016}.
% Since the 10--line threshold is already the default configuration for
% NiCad, this filter is applied to Simian only (Simian's default
% configuration has a minimum clone size of 6 lines).
%The \emph{irrelevant methods filter} removes clones of
%\verb|hashCode()| methods and getters/setters which are almost always
%false clones. 
The second filter, \emph{similarity threshold}, applies
only to NiCad clone pairs since Simian does not provide a similarity
configuration. The last filter, \emph{good/ok pairs}, removes the
clone pairs that already exist in the agreed clone sets.

@@

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{classification_process}
	\caption{Online code clone classification process}
	\label{fig:classification_process}
\end{figure}

@@

\textbf{To answer RQ1, with the four configurations of Simian and
  NiCad, we found online code clones in 1,086 ($S_D$), 1,531 ($S_E$),
  1,392 ($N_D$) and 12,886 ($N_E$) Stack Overflow code snippets. They
  are associated with 92, 111, 82 and 88 Qualitas projects
  respectively, i.e.~most Qualitas projects share similar code with
  Stack Overflow code snippets.}

\FIXME{Do you think we should report at this level or in more details 
	into $S_D$--$N_D$, $S_D$--$N_E$, $S_E$--$N_D$, $S_E$--$N_E$??}

However, using Bellon's criteria for matching clone pairs, only
0.1\textperthousand~of all pairs are agreed by two tool/configuration
combinations. For the 2,308 \textit{good} pairs, there are 92 Stack Overflow snippets
which are associated with 66 Qualitas projects. The 11,749 \textit{ok} 
pairs are clones between 136 Stack Overflow snippets and 39 Qualitas 
projects.

Moreover, for the disagreed pairs, we found 17,081 clone pairs reported by $S_D$
are clones between 471 Stack Overflow snippets and 76 Qualitas projects and 
88 $N_D$ clone pairs are clones between 77 Stack Overflow snippets and 29
Qualitas projects.

% FIXME
% However, as it is well known that the precision of clone detectors is
% not very good, it is clear that the above numbers may not be
% representative for real code clones and we ...

@@

%\FIXME{Why equals here but not hashcode? Why isn't it the same
%  irrelevant methods filter?}

We rely on a manual study to qualitatively investigate the patterns of
online code cloning. To achieve this, we classified all 31,946
selected clone pairs according to the process shown in
\Cref{fig:classification_process}.  Before performing the manual
classification, we created and used an automatic classifier 
to classify {\small\texttt{equals()}}, 
{\small\texttt{hashCode()}} and getters/setters. As shown in
\Cref{tab:online_clone_classification_results}, the automatic
classifier helped us classified and captured 28,314 clone pairs into
pattern \textbf{BP}.

There were 3,632 pairs left for the manual check. The first author,
who has been working on clone detection research for two years, took
the role of the main investigator performing a manual classification
of the 3,632 clone pairs. By consulting the cloning patterns, the main
investigator went through each clone pair candidate, looked at the
clones, and chose the most appropriate cloning pattern for the pair.

To mitigate the human errors of the manual classification, the second
author took the role of the validating investigator, performing a
validation on 10\% (363 pairs) of the clone pairs judged by the main
investigator. After the validation, the classifications from the two
investigators were compared and 64 conflicts were found. The two
investigators discussed and resolved 61 of them while the 3 conflicts
were resolved by involving the third author. The classification
results are shown in \Cref{tab:classification_good_o}.

To answer RQ2, the classification results are explained and discussed
below.

@@

%\FIXME{You are using the complete number of pairs in a project instead
%  of the outdated pairs!!!}
 %Some of the clone pairs overlap with each other so we group them in the same row. 
We discovered 64 outdated online clone pairs out of 112 pairs. As
shown in \Cref{fig:outdated}, \textsf{spring}
have the highest number of 17 outdated pairs, followed by 7 from
\textsf{hibernate} and \textsf{hadoop}, and 6 from \textsf{junit}. Besides the example of
outdated code in the \textsf{hadoop}'s
{\small{\texttt{WritableComparator.java}}} shown in
\Cref{fig:before-after}, we also found a few outdated code elements
which contained a large amount of modifications. For example, the code
snippet in Stack Overflow post 23520731 is a copy of
{\small{\texttt{SchemaUpdate.java}}} in \textsf{hibernate}. The code
has been heavily modified on 5 February 2016.

@@

\begin{table*}
	\centering
	\caption{Examples of the outdated QS online clones}
	\label{tab:stale_code_details}
	%\small
	\resizebox{2.1\columnwidth}{!}{%
		\begin{tabular}{l|l|l|l|p{5.1cm}|r|r|l|c|l}
		 \hline
		 \multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ 
		 \hline
		 Post & Date & Project & Ver. & File & Start & End & Date & Type$^*$ & Date \\
		 \hline
		 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
		 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{S} & 5-Feb-16 \\
		 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
		 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{R} & 26-Jun-13 \\
		 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{D} & 20-May-11 \\
		 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
		 \hline 
		 \multicolumn{10}{l}{{\footnotesize * \textit{S}=modified/added/deleted statements, \textit{D}=file deletion,  \textit{R}=method rewriting}}
		\end{tabular} %
	}
\end{table*}

@@

\begin{table}[]
	\centering
	\caption{License mapping of the online clones (file-level) in
          QS, UD, and EX}
	\label{tab:license_abc}
	\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|p{2cm}l|rrr}
		\hline
		Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & EX & UD \\
		\hline
		Compatible & Apache2 & Apache2 &  0 & 0  & 1\\
		License	& EPLv1 & EPLv1 &  1 & 0 & 1\\
		& Sun (proprietary) & Sun (proprietary) & 0 & 1 & 0\\
		& MIT-like & MIT-like & 0 & 1 & 0\\
		& No license & CC BY-NC-SA & 0 & 5 & 0 \\
		& No license & No license & 5 & 4 & 21 \\
		\hline
		\multicolumn{3}{l|}{Total} & 6 & 11 & 23 \\
		\hline
	    Incompat. & BSD3 & GPLv2+ & 0 & 0 & 1 \\
		License	& No license & AGPLv3/3+ & 1 & 0 & 2 \\
		& No license & Apache-2 & 41 & 5 & 23 \\
		& No license & BSD3 & 3 & 4 & 28 \\
		& No license & CDDL or GPLv2 & 1 & 0 & 58 \\
		& No license & CDDLv1 & 0 & 1 & 0 \\
		& No license & EPLv1 & 7 & 0 & 10 \\
		& No license & GPLv2/2+/3+ & 2 & 62 & 32 \\
		& No license & LGPLv2/2.1+/3+ & 24 & 0 & 32 \\
		& No license & MPLv1.1 & 0 & 0 & 1 \\
		& No license & spdxBSD3 & 0 & 0 & 10 \\
		& No license & SPLv1 & 0 & 1 & 0 \\
		& No license & Unknown & 0 & 3 & 3 \\
		& spdxBSD3 & AGPLv3+ & 0 & 0 & 2 \\
		\hline
		\multicolumn{3}{l|}{Total} &  79 & 76 & 202 \\
		\hline
	\end{tabular} %
%}
\end{table}

>>>>

%\overfullrule1ex

@@

\begin{abstract}
  % We studied online code clones on the popular programming Q\&A
  % website, Stack Overflow, and their issues on outdated code and
  % software licensing violations. 
  Online code clones are code fragments that are copied from software
  projects or online sources to Stack Overflow as examples in
  questions and answers.
  % They can be discovered by using code clone
  % detectors, yet they are inherently different from normal code clones
  % in software projects in several aspects. 
  Due to an absence of a checking mechanism after the code has been
  copied to Stack Overflow, online code clones may suffer from
  becoming outdated or violating the original software license.
  % Moreover, we also found that majority of online code clones do not
  % contain the license of their originals.
  We present a study incorporating several state-of-the-art tools and
  techniques to automatically extract, prioritise, and filter
  315,786,118 detected online clone pairs between 144,064 Java code
  snippets on Stack Overflow and 111 Java open source projects in the
  curated Qualitas corpus. We discovered and investigated 51,926
  non-trivial online clone candidates. Our study revealed that 64 out
  of 112 clones with strong evidence of copying from a Qualitas
  project to Stack Overflow are outdated. Furthermore, we found 357
  code snippets on Stack Overflow that violate the license of their
  original software.
  % These snippets are questionable for reuse.
  Our study is among the first to address the problem of
  outdated and license-violating code snippets on Stack Overflow.
\end{abstract}

@@

\begin{figure*}
	\begin{lstlisting}
          /* Code in Stack Overflow post ID 22315734 */                  /* WritableComparator.java (2016-09-26) */
          public int compare(byte[] b1,int s1,int l1,                    public int compare(byte[] b1,int s1,int l1,
                             byte[] b2,int s2,int l2) {                                     byte[] b2,int s2,int l2) {
            try {                                                          try {
              buffer.reset(b1,s1,l1); /* parse key1 */                       buffer.reset(b1,s1,l1); /* parse key1 */
              key1.readFields(buffer);                                       key1.readFields(buffer);
              buffer.reset(b2,s2,l2); /* parse key2 */                       buffer.reset(b2,s2,l2); /* parse key2 */
              key2.readFields(buffer);                                       key2.readFields(buffer);
            } catch (IOException e) {                                        buffer.reset(null,0,0); /* clean up reference */
              throw new RuntimeException(e);                               } catch (IOException e) {
            }                                                                throw new RuntimeException(e);
            return compare(key1,key2); /* compare them */                  }
          }                                                                return compare(key1, key2); /* compare them */
	                                                                       }
	\end{lstlisting}\vspace{-2ex}
	\caption{A motivating example of the two code fragments of
          {\small\texttt{WritableComparator.java}}. The one from the
          Stack Overflow post 22315734 (left) is outdated when compared to
          its latest version in the \textsf{hadoop} code base
          (right).}
	\label{fig:before-after}
\end{figure*}

@@

While research has mostly focused on reusing code snippets \emph{from}
Stack Overflow (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less work
has been conducted on finding the origins of code examples copied
\emph{to} Stack Overflow and problems of reusing them such as outdated
code and software licensing violations. This paper fills this gap and
makes the following primary contributions:

@@

\noindent%
The \textit{good-value}  and the \textit{ok-value}  of two clone pairs are defined as
%\squeezeup
\begin{align*}
	good(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = min(overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1), \\ overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2))
\end{align*}
\begin{align*}
	ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) = min(max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1),~~ \\ contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1)),~
	\\ max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2),~~ \\contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2)))
\end{align*}

@@

Even choosing only the default configurations, the number of disagreed
clone pair candidates is still too large for manual inspection (67,570
for $S_D$ and 632,855 pairs for $N_D$). We applied three filters: clone
size, irrelevant methods, similarity threshold, and good/ok pairs. For
the \emph{clone size filter}, we raised the minimum clone size to 10 lines
since larger clones are more interesting, while smaller ones tend to
be false clones~\cite{Saini2016}.
% Since the 10--line threshold is already the default configuration for
% NiCad, this filter is applied to Simian only (Simian's default
% configuration has a minimum clone size of 6 lines).
The second filter, \emph{similarity threshold}, applies
only to NiCad clone pairs since Simian does not provide a similarity
configuration. The last filter, \emph{good/ok pairs}, removes the
clone pairs that already exist in the agreed clone sets.

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{classification_process}
	\caption{Online code clone classification process}
	\label{fig:classification_process}
\end{figure}

@@

% \FIXME{Do you think we should report at this level or in more details 
% 	into $S_D$--$N_D$, $S_D$--$N_E$, $S_E$--$N_D$, $S_E$--$N_E$??}
% I don't think there is a need.

\begin{table}
\caption{FIXME Maybe merge with Table 7?}
\label{tab:snippets}
\centering
\begin{tabular}{l|rrr}
  & Pairs & Snippets & Projects \\
\hline
\textit{good} & 2,308 & 92 & 66 \\
\textit{ok'} & 11,749 & 136 & 39 \\
$S_D'$ & 17,081 & 471 & 76 \\
$N_D'$ & 88 & 77 & 29 \\
\hline
Total & 31,946 & FIXME & FIXME
\end{tabular}
\end{table}

However, using Bellon's criteria for matching clone pairs, only
0.1\textperthousand~of all pairs are agreed by two tool/configuration
combinations. As shown in FIXME, for the 2,308 \textit{good} pairs,
there are 92 Stack Overflow snippets which are associated with 66
Qualitas projects. The 11,749 \textit{ok'} pairs are clones between
136 Stack Overflow snippets and 39 Qualitas projects.  Moreover, for
the disagreed pairs, we found 17,081 clone pairs reported by $S_D'$
are clones between 471 Stack Overflow snippets and 76 Qualitas
projects and 88 $N_D'$ clone pairs are clones between 77 Stack
Overflow snippets and 29 Qualitas projects. In total we found that the
manually investigated 31,946 clones pairs are clones between FIXME
Stack Overflow snippets and FIXME Qualitas projects.

\textbf{To answer RQ1, with the four configurations of Simian and
  NiCad, we found most Qualitas projects to share similar code with
  Stack Overflow code snippets. When onlly considering the manually
  investigated snippets, FIXME}

\FIXME{Should we have removed the AC clones right at the beginning?}

@@

We rely on a manual study to qualitatively investigate the patterns of
online code cloning. To achieve this, we classified all 31,946
selected clone pairs according to the process shown in
\Cref{fig:classification_process}.  Before performing the manual
classification, we created and used an automatic classifier 
to classify {\small\texttt{equals()}}, 
{\small\texttt{hashCode()}} and getters/setters. As shown in
\Cref{tab:online_clone_classification_results}, the automatic
classifier helped us to classify 28,314 clone pairs into
pattern \textbf{BP}.

There were 3,632 pairs left for the manual check. The first author,
who has been working on clone detection research for two years, took
the role of the main investigator performing a manual classification
of the 3,632 clone pairs. By consulting the cloning patterns, the main
investigator went through each clone pair candidate, looked at the
clones, and chose the most appropriate cloning pattern for the pair.
%
To mitigate the human errors of the manual classification, the second
author took the role of the validating investigator, performing a
validation on 10\% (363 pairs) of the clone pairs judged by the main
investigator. After the validation, the classifications from the two
investigators were compared and 64 conflicts were found. The two
investigators discussed and resolved 61 of them while the 3 conflicts
were resolved by involving the third author. The classification
results are shown in \Cref{tab:classification_good_o} and explained in
the following.

@@

We discovered 64 outdated online clone pairs out of 112 pairs. As
shown in \Cref{fig:outdated}, \textsf{spring} has the highest number
of 17 outdated pairs, followed by 7 from \textsf{hibernate} and
\textsf{hadoop}, and 6 from \textsf{junit}. Besides the example of
outdated code in % \textsf{hadoop}'s
{\small{\texttt{WritableComparator.java}}} 
from \textsf{hadoop} shown in
\Cref{fig:before-after}, we also found a few outdated code elements
which contained a large amount of modifications. For example, the code
snippet in Stack Overflow post 23520731 is a copy of
{\small{\texttt{SchemaUpdate.java}}} in \textsf{hibernate}. The code
has been heavily modified on 5 February 2016.

@@

\begin{table*}
	\centering
	\caption{Examples of the outdated QS online clones}
	\label{tab:stale_code_details}
	%\small
	%\resizebox{\textwidth}{!}{%
		\begin{tabular}{cc|lcp{5.15cm}@{}rrc|c@{}c}
		 \hline
		 \multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ 
		 \hline
		 Post & Date & Project & Ver. & File & Start & End & Date & Type$^*$ & Date \\
		 \hline
		 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
		 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{S} & 5-Feb-16 \\
		 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
		 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{R} & 26-Jun-13 \\
		 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{D} & 20-May-11 \\
		 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
		 \hline 
		 \multicolumn{10}{l}{{\footnotesize * \textit{S}:
                  modified/added/deleted statements, \textit{D}: file
                  has been deleted,  \textit{R}: method has been
                  rewritten completely}}
		\end{tabular} %
	%}
\end{table*}

@@

\begin{table}[]
	\centering
	\caption{License mapping of  online clones (file-level)}
	\label{tab:license_abc}
	\small
	%\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|p{1.95cm}l|rrr}
		\hline
		Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & EX & UD \\
		\hline
		Compatible & Apache2 & Apache2 &  0 & 0  & 1\\
		License	& EPLv1 & EPLv1 &  1 & 0 & 1\\
		& Sun (proprietary) & Sun (proprietary) & 0 & 1 & 0\\
		& MIT-like & MIT-like & 0 & 1 & 0\\
		& No license & CC BY-NC-SA & 0 & 5 & 0 \\
		& No license & No license & 5 & 4 & 21 \\
		\hline
		\multicolumn{3}{l|}{Total} & 6 & 11 & 23 \\
		\hline
	    Incompat. & BSD3 & GPLv2+ & 0 & 0 & 1 \\
		License	& No license & AGPLv3/3+ & 1 & 0 & 2 \\
		& No license & Apache-2 & 41 & 5 & 23 \\
		& No license & BSD3 & 3 & 4 & 28 \\
		& No license & CDDL or GPLv2 & 1 & 0 & 58 \\
		& No license & CDDLv1 & 0 & 1 & 0 \\
		& No license & EPLv1 & 7 & 0 & 10 \\
		& No license & GPLv2/2+/3+ & 2 & 62 & 32 \\
		& No license & LGPLv2/2.1+/3+ & 24 & 0 & 32 \\
		& No license & MPLv1.1 & 0 & 0 & 1 \\
		& No license & spdxBSD3 & 0 & 0 & 10 \\
		& No license & SPLv1 & 0 & 1 & 0 \\
		& No license & Unknown & 0 & 3 & 3 \\
		& spdxBSD3 & AGPLv3+ & 0 & 0 & 2 \\
		\hline
		\multicolumn{3}{l|}{Total} &  79 & 76 & 202 \\
		\hline
	\end{tabular} %
%}
\end{table}
